*Prochlorococcus marinus* responses to light and oxygen

### 2024-06-10 Code/Manuscript_O2.Rmd
Fixed data availability section

All data are available on the figshare data repository (10.6084/m9.figshare.25959061).

Annotated code for data import, transformations and analyses are
available at
<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Code>.

>>>>

All data and annotated code for data import, transformations and analyses are
available at are available on the figshare data repository (DOI: 10.6084/m9.figshare.25959061).
